Neuroecon Poster Figures

### 2017-10-04 code/NeuroeconPoster.Rmd
cont working on poster

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(stringr)
library(plotly)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
options(scipen = 1, digits = 4, width = 500)
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
```

@@

boot_df_poster = boot_df_poster %>%
  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
  rename(icc = icc.x, point_est = icc.y)
```

@@

@@

@@

@@

@@

@@

Table for task reliabilities by cognitive construct

@@

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(stringr)
library(plotly)
library(xtable)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
options(scipen = 1, digits = 4, width = 500)
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
```

@@

boot_df_poster = boot_df_poster %>%
  left_join(rel_df[,c("dv", "icc")], by = "dv") %>%
  rename(icc = icc.x, point_est = icc.y)

#Manual correction
boot_df_poster = boot_df_poster %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", task))
```

@@

```{r warning=FALSE, message=FALSE}
p7 <- ggplot_build(rel_df %>%
               ggplot(aes(icc, fill=task)) +
               geom_histogram(position = 'identity', alpha=0.5))$data[[1]] %>%
  mutate(task=ifelse(as.character(fill) == "#00BFC4", "task", "survey")) %>%
  ggplot(aes(x,y, fill=task))+
  geom_bar(stat='identity', position='identity', alpha=0.5)+
  xlab('ICC')+
  ylab('Count')+
  theme_bw()+
  theme(legend.position="bottom",
        legend.title = element_blank(),
        legend.text= element_text(size=30),
        axis.text.x = element_text(size=20),
        axis.text.y = element_text(size=20),
        axis.title.x = element_text(size = 30),
        axis.title.y = element_text(size = 30))

ggsave('Point_Est_Hist_Poster.jpg', plot = p7, device = "jpeg", path = "../output/figures/", width = 10, height = 10, units = "in")
```

@@

```{r}
summary(lm(icc ~ task, data=rel_df))
```

@@

```{r}
rel_df
```

@@

```{r warning=FALSE, message=FALSE}
survey_labels = fig_data %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  distinct(task_group, .keep_all=T) %>%
  select(-dv, -var, -measure_description, -retest_reliability, -type, -days, -sample_size, -reference) %>%
  filter(task == "survey")

tmp = rel_df %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "survey") %>%
  left_join(survey_labels, by = "task_group") %>%
  na.omit()

summary(lm(icc ~ num_all_trials,data = tmp))
```

@@

```{r}
survey_rel_table = boot_df %>%
  filter(task == "survey") %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  group_by(task_group) %>%
  summarise(min_icc = min(icc),
            mean_icc = mean(icc),
            max_icc = max(icc)) %>%
  mutate(task_group = gsub("_", " ", task_group))

names(survey_rel_table) <- c("Survey", "Min ICC", "Mean ICC", "Max ICC")
write.csv(survey_rel_table, "../output/figures/survey_rel_table.csv")
```

@@

```{r warning=FALSE, message=FALSE}
measure_labels <- read.csv('../input/measure_labels.csv')

measure_labels = measure_labels %>%
  select(dv, task, variable_type, ddm_task, num_all_trials)%>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  distinct(task_group, .keep_all=T) %>%
  filter(task == "task") %>%
  select(-dv, -var, -task)

tmp = rel_df %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  filter(task == "task") %>%
  left_join(measure_labels, by = "task_group") %>%
  na.omit()

summary(lm(icc ~ num_all_trials,data = tmp))
```

```{r}
task_rel_table = boot_df %>%
  filter(task == "task") %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  group_by(task_group) %>%
  summarise(min_icc = min(icc),
            mean_icc = mean(icc),
            max_icc = max(icc)) %>%
  mutate(task_group = gsub("_", " ", task_group))

names(task_rel_table) <- c("Task", "Min ICC", "Mean ICC", "Max ICC")
write.csv(task_rel_table, "../output/figures/task_rel_table.csv")
```

@@

```{r}
tmp %>%
  filter(ddm_task == 1) %>%
